Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex
starting 2.1

\bo{I think this organization is great!}

%\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$. It was just a typo in this introduction of regret.  I don't mind changing it, but I like the semicolon.  I think that might be Bo's class influencing me haha.  My preferences aren't super strong one way of the other here.}\jessie{Missing codim; in flats definition is fine?}
\raf{While ugly, for now let's use:} ``\verb|\exploss{L}{u}{p}|''

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} (or label space) $\Y$.
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ outcomes/labels forming $\Y$.
As we focus heavily on conditional distributions $\Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
The probability simplex over $\Y$ is $\simplex$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.

@@

\bo{Rewrote this, Mon Jun 1 a.m.}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

>>>>

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} (or label space) $\Y$.
\raft{To discuss: labels or outcomes?}
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ outcomes/labels forming $\Y$.
As we focus heavily on conditional distributions $\Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
The probability simplex over $\Y$ is $\simplex$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.

@@

%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to
\raft{I like this phrasing -- nicely captures all settings}
solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
